---
title: "PoloniexR"
output: rmarkdown::github_document
---

[![Travis-CI Build Status](https://travis-ci.org/VermeirJellen/PoloniexR.svg?branch=master)](https://travis-ci.org/VermeirJellen/PoloniexR)

This package aims to provide a user-friendly R wrapper on top of the Poloniex (Cryptocurrency Trading) REST API. Results are converted into R datastructures and are returned to the users in a more intuitive manner.

Installation:

```{r eval=FALSE}
# install.packages("devtools"")
devtools::install_github("VermeirJellen/PoloniexR")
```

## PoloniexPublicAPI / PoloniexTradingAPI

A ```PoloniexPublicAPI``` object can be created as follows:

``` poloniex.public <- PoloniexPublicAPI()```

Methods Provided:

 - ```ReturnTicker```
 - ```Return24hVolume```
 - ```ReturnOrderBook```
 - ```ReturnTradeHistory```
 - ```ReturnChartData```
 - ```ReturnCurrencies```
 - ```ReturnLoanOrders```
 
A ```PoloniexTradingAPI``` object can be created as follows:

``` poloniex.trading <- PoloniexTradingAPI(key, secret) ```

Methods Provided:

 - **ProcessTradingRequest()**: Allows the users to call any of the trading API methods that are provided by Poloniex.
 - ```ReturnBalances```
 - ```ReturnCompleteBalances```
 
Todo: Higher level methods can potentially be wrapped on top of the ```ProcessTradingRequest``` method (as was done for the ```ReturnBalances``` and ```ReturnCompleteBalances``` functions).

**!! EXAMPLES BELOW !!**

### PUBLIC API - EXAMPLES

#### ReturnTicker

Run ```?ReturnTicker``` for additional function documentation.

```{r message=FALSE}
library(PoloniexR)
poloniex.public <- PoloniexPublicAPI()
ticker.info     <- ReturnTicker(poloniex.public)
head(ticker.info)
```



#### Return24hVolume

Run ```?Return24hVolume``` for additional function documentation.

```{r message=FALSE}
poloniex.public <- PoloniexPublicAPI()
volume.info <- Return24hVolume(poloniex.public)
head(volume.info$volume.pairs)

volume.info$volume.totals
```

#### ReturnOrderBook

Run ```?ReturnOrderBook``` for additional function documentation.

```{r message=FALSE}
pair       <- "BTC_NXT"
depth      <- 10
order.book <- ReturnOrderBook(poloniex.public,
                              pair  = pair,
                              depth = depth)
head(order.book$bid)
head(order.book$ask)
order.book$frozen
order.book$seq

pair       <- "all"
depth      <- 10
order.book <- ReturnOrderBook(poloniex.public,
                              pair  = pair,
                              depth = depth)

order.book$BTC_ETH$bid
order.book$BTC_ETH$ask
order.book$BTC_ETH$frozen
order.book$BTC_ETH$seq
```

#### ReturnTradeHistory

Run ```?ReturnTradeHistory``` for additional function documentation.

```{r message=FALSE}
Sys.setenv(tz="UTC")
pair   <- "BTC_ETH"
from   <- as.POSIXct("2017-07-01 00:00:00 UTC")
to     <- as.POSIXct("2017-07-04 00:00:00 UTC")

trades.data <- ReturnTradeHistory(theObject = poloniex.public,
                                  pair      = pair,
                                  from      = from,
                                  to        = to)

tail(trades.data)
```

#### ReturnChartData

Run ```?ReturnChartData``` for additional function documentation.

```{r message=FALSE}
Sys.setenv(tz="UTC")
pair    <- "BTC_ETH"
from    <- as.POSIXct("2015-01-01 00:00:00 UTC")
to      <- as.POSIXct("2018-04-09 00:00:00 UTC")
period  <- "4H"

chart.data <- ReturnChartData(theObject = poloniex.public,
                              pair      = pair,
                              from      = from,
                              to        = to,
                              period    = period)

tail(chart.data)

# install.packages("quantmod")
library(quantmod)
chart.plot <- chart_Series(chart.data[, "close"],
                           type   = "line",
                           name   = "BTC_ETH",
                           subset = "201705/201708")
chart.plot <- add_MACD()
chart.plot <- add_BBands()
chart.plot <- add_RSI()
chart.plot

```

#### ReturnCurrencies

Run ```?ReturnCurrencies``` for function additional function documentation.

```{r message=FALSE}
currencies <- ReturnCurrencies(poloniex.public)
head(currencies)
```

#### ReturnLoanOrders

Run ```?ReturnLoanOrders``` for additional function documentation.

```{r message=FALSE}
currency        <- "BTC"
loan.orders     <- ReturnLoanOrders(poloniex.public,
                                    currency = currency)
head(loan.orders$offers)
head(loan.orders$demands)
```

#### GET / SET public API URL and command Strings.

Note: Changing these settings is only useful if Poloniex makes changes to the base URL and/or command strings in the future. If nothing changes, object construction can remain default.

```{r message=FALSE}
library(PoloniexR)

poloniex.public <- PoloniexPublicAPI() # Default constructor
GetPoloniexPublicURL(poloniex.public)

poloniex.public <- PoloniexPublicAPI(base.url                     = "https://not_working/public?")
poloniex.public <- SetPoloniexPublicURL(poloniex.public, base.url = "https://poloniex.com/public?")
GetPoloniexPublicURL(poloniex.public)

GetPoloniexPublicCommands(poloniex.public)
commands.new <- list(returnTicker    = "returnTicker.new",
                     return24hVolume = "return24hVolume.new")

# missing commands are kept default
poloniex.public <- SetPoloniexPublicCommands(poloniex.public,
                                             commands = commands.new)
GetPoloniexPublicCommands(poloniex.public)
```



### TRADING API - EXAMPLES

Trading should be enabled in your Poloniex settings and you should have access to your account key / secret in order to construct the ```PoloniexTradingAPI``` object. Internally, all calls to the trading API are sent via HTTP POST. The POST data itself is signed with your key's secret according to the HMAC-SHA512 method.


#### ReturnBalances

Wrapper on top of ```ProcessTradingRequest``` to fetch account balance info. Run ```?ReturnBalances``` for additional info.

```{r eval=FALSE}
key    = your.key
secret = your.secret
poloniex.trading <- PoloniexTradingAPI(key    = key,
                                       secret = secret)
balances <- ReturnBalances(poloniex.trading)
head(balances)
```

#### ReturnCompleteBalances

Wrapper on top of ```ProcessTradingRequests``` to fetch complete (margin, lending, ..) account balance info. Run ```?ReturnCompleteBalances``` for additional info.

```{r eval=FALSE}
balances <- ReturnCompleteBalances(poloniex.trading)
head(balances)

balances <- ReturnCompleteBalances(poloniex.trading, all.balances=TRUE)
head(balances)
```

#### ProcessTradingRequest

This function allows the users to call any of the trading functions that are accessible through the Poloniex Trading API. The ```ProcessTradingRequest``` method takes a command string as input argument in combination with a list of additional input arguments that correspond to the particular command in question. Largely untested, but should work just fine.. (todo: test!).

Some examples:

```{r eval=FALSE}
##########################
# returnDepositAddresses #
##########################
?ProcessTradingRequest
deposit.addresses <- ProcessTradingRequest(poloniex.trading,
                                           command = poloniex.trading@commands$returnDepositAddresses)

#########################
# generateNewAddress ####
#########################
new.address <- ProcessTradingRequest(poloniex.trading,
                                     command = poloniex.trading@commands$generateNewAddress,
                                     args    = list(currency = "BTC"))


##############################
# returnDepositsWithdrawals ##
##############################
account.activity <- ProcessTradingRequest(poloniex.trading,
                                          command = poloniex.trading@commands$returnDepositWithdrawals,
                                          args = list(start = as.numeric(as.POSIXct("2017-01-01 00:00:00 UTC"))),
                                                      end   = as.numeric(as.POSIXct("2018-01-01 00:00:00 UTC")))

##############################
### returnOpenOrders #########
##############################
open.orders <- ProcessTradingRequest(poloniex.trading,
                                     command = poloniex.trading@commands$returnOpenOrders,
                                     args    = list(currencyPair = "BTC_ETH"))

open.orders.all <- ProcessTradingRequest(poloniex.trading,
                                         command = poloniex.trading@commands$returnOpenOrders,
                                         args    = list(currencyPair = "all"))


##############################
### Return Trade History #####
##############################
trade.history <-  ProcessTradingRequest(poloniex.trading,
                                        command = poloniex.trading@commands$returnTradeHistory,
                                        args = list(currencyPair = "BTC_ETH",
                                                    start        = as.numeric(as.POSIXct("2017-01-01 00:00:00 UTC"))),
                                                    end          = as.numeric(as.POSIXct("2018-01-01 00:00:00 UTC")))

# no range specified: limit to one day
trade.history.all <-  ProcessTradingRequest(poloniex.trading,
                                            command = poloniex.trading@commands$returnTradeHistory,
                                            args    = list(currencyPair = "all"))


##############################
### ReturnOrderTrades ########
##############################
order.trades <- ProcessTradingRequest(poloniex.trading,
                                      command = poloniex.trading@commands$returnOrderTrades,
                                      args    = list(orderNumber = 1))

##############################
######### Buy ################
##############################
buy.order <- ProcessTradingRequest(poloniex.trading,
                                   command = poloniex.trading@commands$buy,
                                   args    = list(currencyPair      = "BTC_ETH",
                                                  rate              = 0.01,
                                                  amount            = 1,
                                                  immediateOrCancel = 1)) # fillOrKill, postOnly

##############################
######### Sell ###############
##############################
sell.order <- ProcessTradingRequest(poloniex.trading,
                                    command = poloniex.trading@commands$sell,
                                    args    = list(currencyPair      = "BTC_ETH",
                                                   rate              = 0.01,
                                                   amount            = 1))


##############################
######### cancelOrder ########
##############################
cancel.order <- ProcessTradingRequest(poloniex.trading,
                                      command = poloniex.trading@commands$cancelOrder,
                                      args    = list(orderNumber = 1))

##############################
######### moveOrder ##########
##############################
move.order <- ProcessTradingRequest(poloniex.trading,
                                    command = poloniex.trading@commands$moveOrder,
                                    args    = list(orderNumber       = 1,
                                                   rate              = 0.1,
                                                   amount            = 1,
                                                   immediateOrCancel = 1)) # postOnly
```

Other Trade functionality (View Poloniex API documentation):

 - withdraw: ```poloniex.trading@commands$withdraw```
 - returnFeeInfo: ```poloniex.trading@commands$returnFeeInfo```
 - returnAvailableAccountBalances: ```poloniex.trading@commands$returnAvailableAccountBalances```
 - returnTradeableBalances: ```poloniex.trading@commands$returnTradeableBalances```
 - transferBalance: ```poloniex.trading@commands$transferBalance```
 - returnMarginAccountSummary: ```poloniex.trading@commands$returnMarginAccountSummary```
 - marginBuy: ```poloniex.trading@commands$marginBuy```
 - marginSell: ```poloniex.trading@commands$marginSell```
 - getmarginPosition: ```poloniex.trading@getMarginPosition```
 - closeMarginPosition: ```poloniex.trading@closeMarginPosition```
 - createLoanOffer: ```poloniex.trading@commands$createLoanOffer```
 - cancelLoanOffer: ```poloniex.trading@commands$cancelLoanOffer```
 - returnOpenLoanOffers: ```poloniex.trading@commands$returnOpenLoanOffers```
 - returnActiveLoans: ```poloniex.trading@commands$returnActiveLoans```
 - returnLendingHistory: ```poloniex.trading@commands$returnLendingHistory```
 - toggleAutoRenew: ```poloniex.trading@commands$toggleAutoRenew```


#### GETTERS / SETTERS

Same remark as before: Modification of the object fields are only required if and when Poloniex modifies the trading API base URL and/or the command strings. Default constructor can be used for now.

```{r eval=FALSE}
###########################################################
#################### GETTERs / SETTERS ####################
###########################################################

##################
# Get Trading URL#
##################
GetPoloniexTradingURL(poloniex.trading)

##################
# Set Trading URL#
##################
?SetPoloniexTradingURL
poloniex.trading <- PoloniexTradingAPI(trading.base.url = "https://not_working/tradingApi?",
                                       key              = your.key,
                                       secret           = your.secret)

poloniex.trading <- SetPoloniexTradingURL(poloniex.trading,
                                          trading.base.url = "https://poloniex.com/tradingApi?")
GetPoloniexTradingURL(poloniex.trading)

#######################
# Get Trading commands#
#######################
?GetPoloniexTradingCommands
GetPoloniexTradingCommands(poloniex.trading)

#######################
# Set Trading Commands#
#######################
?SetPoloniexTradingCommands
commands.new <- list(returnTradeHistory = "returnTradeHistory.new",
                     withdraw = "withdraw.new")
poloniex.trading <- SetPoloniexTradingCommands(poloniex.trading,
                                               commands = commands.new)

GetPoloniexTradingCommands(poloniex.trading)
commands.new <- list(returnTicker    = "returnTicker.new",
                     return24hVolume = "return24hVolume.new")
poloniex.trading <- SetPoloniexTradingCommands(poloniex.trading,
                                               commands = commands.new)
GetPoloniexPublicCommands(poloniex.public)
```


## Donations

If you find this software useful and/or you would like to see additional extensions or a future release to CRAN, feel free to donate some crypto:

Crypto Addresses:

 - BTC: 1QHtZLZ15Cmj4FPr5h5exDjYciBDhh7mzA
 - LTC: LhKf6MQ7LY1k8YMaAq9z3APz8kVyFX3L2M
 - ETH: 0x8E44D7C96896f2e0Cd5a6CC1A2e6a3716B85B479
 - DASH: Xvicgp3ga3sczHtLqt3ekt7fQ62G9KaKNB

Or preferably, donate some of my favorite coins :)

 - GAME: GMxcsDAaHCBkLnN42Fs9Dy1fpDiLNxSKX1
 - WAVES: 3PQ8KFdw2nWxQATsXQj8NJvSa1VhBcKePaf
 
## Licensing

Copyright 2017 Essential Data Science Consulting ltd. ([EssentialQuant.com](http://essentialquant.com "EssentialQuant") / jellenvermeir@essentialquant.com).
This software is copyrighted under the MIT license: View added [LICENSE](./LICENSE) file.
